\textbf{\sc Towards Deliberative Control of Autonomous Robots}

### 2012-02-19 trunk/setobook.tex
further updates to arch

Authors Rajan and Py are funded by a block grant from the David and
Lucile Packard Foundation to MBARI. Rajan and Py would like to thank
their collaborators at MBARI, J. Ryan, J. Harvey, R. Vrijenhoek,
J. Bellingham. They also thank colleagues at NASA Ames who made \eu
available as open source; specifically M. del Alto, D. Korsmeyer and
S. Zornetzer. We are indebted to N. Muscettola for his ideas and early
work at NASA Ames which forms the basis of this work.

>>>>

Rajan and Py are funded by a block grant from the David and Lucile
Packard Foundation to MBARI. They thank their collaborators J. Ryan,
J. Harvey, R. Vrijenhoek and J. Bellingham at MBARI. In addition they
thank colleagues M. del Alto, D. Korsmeyer and S. Zornetzer at NASA
Ames who made \eu available as open source. The authors are indebted
to N. Muscettola for his ideas and early work at NASA Ames which forms
the basis of this work.
